---
output: 
  github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Overview of the `fuse` package

This package provides `R6` classes for describing functional data with embedding
in various infinite-dimensional Hilbert spaces. Currently, functional data
classes are implemented in Sobolev spaces (including the popular $L^2$ space of
square-integrable functions) and in Bayes space. Operators `+`, `-`, `*`, and `/` as
well as inner product and induced distance are implemented as well.

## Installation

You can install `fuse` from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("astamm/fuse")
```

## Example

```{r setup}
library(fuse)
```

We can for example use the default constructor for `FunctionalData` objects to generate a `FunctionalData` version of the density of the standard normal distribution. If we create it embedded in Sobolev spaces and multiply it by `2`, we obtain the following function:
```{r sobolev}
f <- SobolevData$new()
(2 * f)$plot()
```

This is essentially the original density pointwise multiplied by a factor of `2` which does not result in a density anymore. If instead we embed the density of the standard normal distribution in Bayes space and again multiply it by `2`, we get:
```{r bayes}
g <- BayesData$new()
(2 * g)$plot()
```

This shows a fundamental difference between Sobolev and Bayes spaces. In the latter, adding twice the information content in `g` provides additional information and thus has the effect of diminishing the variance of the resulting distribution which turns out to be another centered normal distribution with smaller variance.
